A new form of transcorrelated Hamiltonian inspired by range-separated DFT

### 2020-12-20 cusp_j/paper/paper.tex
modified stuffs

\begin{abstract}
The present work introduces a new form of explicitly correlated factor in the context of the transcorrelated methods. 
The new correlation factor is obtained from the $r_{12} \approx 0$ mathematical analysis of the transcorrelated Hamiltonian, and its analytical form is obtained such that the scalar part of the effective two-electron potential reproduces at leading order in $1/r_{12}$ the long-range interaction of the range-separated density functional theory. 
The resulting correlation factor is then tuned by a unique parameter $\mu$ which controls both the depth of the coulomb hole and its typical range in $r_{12}$. 
The transcorrelated Hamiltonian obtained with such a new correlation factor as a straightforward analytical expression and its physical contents depends on the same parameter $\mu$: one can continuously change from a non divergent repulsive Hamiltonian potential at large $\mu$ to a purely attractive one at small $\mu$. We investigate the convergence of the eigenvalues and right-eigenvectors of such new transcorrelated Hamiltonian as a function of the basis set and as a function of $\mu$ on a series of two-electron systems. 
We found that the convergence towards the complete basis set is much faster for a quite wide range values of $\mu$. We also propose a computationally cheap way to find a reasonable value of $\mu$ that automatically adapts to the system through its density.  
It should be pointed out that all two-electron integrals can be carried analytically within such approach and the three-electrons terms can be performed using a mixed analytical-numerical integration approach.

@@

\subsection{A new form of Jastrow factor $u(\mu,r_{12})$ mimicking a long-range interaction}
\label{sec:new_j}
\subsubsection{A simple physical picture: the transcorrelated Hamiltonian for the helium atom}
\label{sec:he_htilde}
Let us write the Hamiltonian of the helium atom using the $r_i = \big|{\bf r}_i\big|$ and $ r_{12} = \big|{\bf r}_1 - {\bf r}_2 \big|$ coordinates  
\begin{equation}
 H  = h_c + \frac{1}{r_{12}},
\end{equation}
where 
\begin{equation}
 \begin{aligned}
 \label{def:h_c}
 h_c = &-\frac{1}{2} \sum_{i=1}^2 \bigg(\deriv{}{r_i}{2} + \frac{2}{r_i} \deriv{}{r_i}{} + \frac{2 Z}{r_i}\bigg) \\
     &-\bigg( \deriv{}{r_{12}}{2} + \frac{2}{r_{12}} \deriv{}{r_{12}}{} \bigg) \\
     &-\bigg( \frac{\bd{r_1}}{r_1} \cdot \frac{\bd{r_{12}} }{r_{12}}  \deriv{}{r_1}{} + 
                \frac{\bd{r_2}}{r_2} \cdot \frac{\bd{r_{21}} }{r_{21}}  \deriv{}{r_2}{} \bigg).
 \end{aligned}
\end{equation}
\label{sec:he_j}
Now let us consider the transcorrelated Hamiltonian $\tilde{H}[u]$ obtained by a similarity transformation of the usual Hamiltonian by a Jastrow factor $u(r_{12})$ depending only on $r_{12}$: 
\begin{equation}
 \label{eq:ht_0}
 \begin{aligned}
 \tilde{H}[u]&= e^{-u(r_{12})} H e^{u(r_{12})}.
 \end{aligned}
\end{equation}
The only additional terms arising in $\tilde{H}[u]$ with respect to $H$ are those coming from the action of the differential operator in $r_{12}$,
\begin{equation}
 \mathcal{T}[u] =  -e^{-u(r_{12})}\bigg( \deriv{}{r_{12}}{2} + \frac{2}{r_{12}} \deriv{}{r_{12}}{} \bigg)e^{u(r_{12})}.  
\end{equation}
By defining the following operators 
\begin{equation}
 \label{eq:def_tt}
 \tilde{t}[u] = -2 \deriv{u(r_{12})}{r_{12}}{} \deriv{}{r_{12}}{},
\end{equation}
\begin{equation}
 \label{eq:def_wt}
 \tilde{W}[u] = -\frac{2}{r_{12}} \deriv{u(r_{12})}{r_{12}}{}  , 
\end{equation}
\begin{equation}
 \label{eq:def_wt}
 \tilde{w}[u] = -\deriv{u(r_{12})}{r_{12}}{2} - \bigg( \deriv{u(r_{12})}{r_{12}}{} \bigg)^2, 
\end{equation}
one can write the Similarity transformed Hamiltonian  as
\begin{equation}
 \label{eq:ht_general}
 \tilde{H}[u] = h_c + \frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u] + \tilde{t}[u].
\end{equation}
Therefore, one can see from Eq. \eqref{eq:ht_general} that the two electrons experience a modified scalar potential given by $\frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u]$, and an additional differential operator $\tilde{t}[u]$, 
the latter making $\tilde{H}[u]$ non-hermitian.

\subsubsection{The working equation for $u(\mu,r_{12})$ inspired by RSDFT}
Having established the form of $\tilde{H}[u] $ in Eq. \eqref{eq:ht_general}, one can notice that the leading order terms in $1/r_{12}$ are $\frac{1}{r_{12}}  + \tilde{W}[u]$. We want now to impose the form of $u(r_{12})$ such that it mimics, at leading order in $1/r_{12}$, the long-range effective interaction entering in the effective Hamiltonian of the RS-DFT (see Eq. \eqref{eq:cusp_psi_mu_0} in Appendix \ref{sec:cusp}). 
Mathematically, this conditions implies that 
\begin{equation}
 \begin{aligned}
 \label{def_j_00}
 \tilde{W}[u] + \frac{1}{r_{12}}&= \frac{\text{erf}(\mu r_{12})}{r_{12}} \\ 
\Leftrightarrow -\frac{2}{r_{12}} \deriv{u(r_{12},\mu)}{r_{12}}{} + \frac{1}{r_{12}} & = \frac{\text{erf}(\mu r_{12})}{r_{12}}, 
 \end{aligned}
\end{equation}
which is equivalent to 
\begin{equation}
 \label{def_j_0}
 \deriv{u(r_{12},\mu)}{r_{12}}{} = \frac{1 - \text{erf}(\mu r_{12})}{2}.
\end{equation}
The solution to Eq. \eqref{def_j_0} is 
\begin{equation}
 \label{eq:def_j}
 u(r_{12};\mu) = \frac{1}{2}r_{12}\bigg( 1 - \text{erf}(\mu r_{12})  \bigg) - \frac{1}{2\sqrt{\pi}\mu}e^{-(r_{12}\mu)^2},
\end{equation}
which defines the new Jastrow factor $u(r_{12};\mu)$ which depends on a unique parameter $\mu$.  
The associated transcorrelated Hamiltonians obtained with $u(r_{12};\mu)$ is also controlled by $\mu$
\begin{equation}
 \label{eq:def_ht_mu}
 \tilde{H}[\mu] = e^{-u(r_{12};\mu)} H e^{u(r_{12};\mu)}. 
\end{equation}
Therefore, the right- and left-eigenvectors of $\tilde{H}[\mu]$ depends only on $\mu$, and the right-eigenvectors satisfy 
\begin{equation}
 \tilde{H}[\mu] \phimui(\br{}_{1},\br{}_{2}) = E_i \phimui(\br{}_{1},\br{}_{2}), 
\end{equation}
where $E_i$ is the exact $i$-th eigenvalue of the physical Hamiltonian. The fact that $\tilde{H}[\mu]$ and $H$ have the same spectrum originates from the properties of the similarity transformation. Nevertheless, once projected in an incomplete basis set, $\tilde{H}[\mu]$ and $H$ might not have the same eigenvalues.

@@

\subsection{The general analytical form of  $\tilde{H}[\mu]$ and some of its properties}
\label{sec:ht_general}
\subsubsection{General analytical form of $\tilde{H}[\mu]$ for a $N$-electron system}
Having established the analytical expression of $u(r_{12};\mu)$, one can derive the expression of the associated transcorrelated Hamiltonian for a general $N$-electron system.  
Using the general form of the transcorrelated Hamiltonian of Eq. (2) in Ref. \onlinecite{CohLuoGutDobTewAla-JCP-19} and using $u(r_{12},\mu)$ as Jastrow factor gives 
\begin{equation}
 \begin{aligned}
 \label{ht_def_g}
 \tilde{H}[\mu] &\equiv e^{-\hat{\tau}_\mu} \hat{H} e^{\hat{\tau}_\mu} \\ 
                &= H + \big[ H,\hat{\tau}_\mu \big] + \frac{1}{2}\bigg[ \big[H,\hat{\tau}_\mu\big],\hat{\tau}_\mu\bigg],
 \end{aligned}
\end{equation}
with $\hat{\tau}_\mu = \sum_{i<j}u(r_{ij},\mu)$ and $\hat{H} = \sum_i -\frac{1}{2} \nabla^2_i + v(\br{}_i) + \sum_{i<j} \frac{1}{r_{ij}}$. 
Eq. \eqref{ht_def_g} leads to the following transcorrelated Hamiltonian 
\begin{equation}
 \begin{aligned}
 \label{ht_def_gu}
 \tilde{H}[\mu] & = H - \sum_{i<j} \hat{K}_\mu(\bri{i},\bri{j}) - \sum_{i<j<k} \hat{L}_\mu(\bri{i},\bri{j},\bri{k}),
 \end{aligned}
\end{equation}
where the effective two- and three-body operators $\hat{K}_\mu(\bri{1},\bri{2})$ and $\hat{L}_\mu(\bri{1},\bri{2},\bri{3})$ are defined as
\begin{equation}
 \begin{aligned}
 \label{def_k}
  \hat{K}_\mu(\bri{1},\bri{2})  = \frac{1}{2} \bigg( &\Delta_1 u(r_{12},\mu) + \Delta_2 u(r_{12},\mu) \\
                                               + &\big(\nabla_1 u(r_{12},\mu) \big) ^2 + \big(\nabla_1 u(r_{12},\mu) \big) ^2 \bigg) \\
                                               + &\nabla_1 u(r_{12},\mu) \cdot \nabla_2 + \nabla_2 u(r_{12},\mu)\cdot \nabla_1,
 \end{aligned}
\end{equation}
\begin{equation}
 \begin{aligned}
 \label{def_k}
  \hat{L}_\mu(\bri{1},\bri{2},\bri{3})  = & \nabla_1 u(r_{12},\mu) \cdot \nabla_1 u(r_{13},\mu) + \nabla_2 u(r_{21},\mu) \cdot \nabla_2 u(r_{23},\mu)  \\
                                     + & \nabla_3 u(r_{13},\mu) \cdot \nabla_3 u(r_{32},\mu).
 \end{aligned}
\end{equation}

@@

\subsubsection{A special case of $\tilde{H}[\mu]$ which mimics the FROGG}
As the Jastrow factor $u(r_{12},\mu)$ for $\mu=\mfrogg$ is very close to the FROGG, we can also compare the scalar effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ with that obtained with the transcorrelated Hamiltonian obtained with the FROGG. 
The latter is simply defined as 
\begin{equation}
 \label{eq:tn_htilde}
 \tilde{H}_{\text{TN}} = e^{-\hat{\tau}_{\text{TN}}}H e^{\hat{\tau}_{\text{TN}}},
\end{equation}
with $\hat{\tau}_{\text{TN}} = \sum_{i<j} u^\text{TN}(r_{ij})$. 
This leads to the following transcorrelated Hamiltonian 
\begin{equation}
 \label{eq:tn_htilde_2}
  \tilde{H}_{\text{TN}} = H + \sum_{i<j} \bigg( \tilde{\mathcal{W}}^\text{TN}_{ee}(r_{ij}) + \tilde{t}^\text{TN} \bigg) - \sum_{i<j<k} \hat{L}^\text{TN}(\bri{1},\bri{2},\bri{3})
\end{equation}
where 
\begin{equation}
 \label{eq:_wee_frogg}
 \tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})= \frac{1}{r_{12}}-\Delta_1 u^{\text{TN}}(r_{12}) - \big(\nabla_1 u^{\text{TN}}(r_{12}) \big) ^2, 
\end{equation}
\begin{equation}
 \begin{aligned}
 \tilde{t}^\text{TN} = &\nabla_1 u^\text{TN}(r_{12}) \cdot \nabla_2 + \nabla_2 u^\text{TN}(r_{12})\cdot \nabla_1,
 \end{aligned}
\end{equation}
\begin{equation}
 \begin{aligned}
 \label{def_k}
  \hat{L}^{\text{TN}}(\bri{1},\bri{2},\bri{3})  = & \nabla_1 u^\text{TN}(r_{12}) \cdot \nabla_1 u^\text{TN}(r_{12}) \\ 
                                     + & \nabla_2 u^\text{TN}(r_{21}) \cdot \nabla_2 u^\text{TN}(r_{23})  \\
                                     + & \nabla_3 u^\text{TN}(r_{31}) \cdot \nabla_3 u^\text{TN}(r_{32}).
 \end{aligned}
\end{equation}
As apparent from Fig. \ref{fig_wee_frogg} where $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ and $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ are represented, while the latter is perfectly smooth for all $r_{12}$, the former strongly oscillates near $r_{12}=0$ between positive and negative values and is not bounded for $r_{12}=0$. 
Such behaviour of $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ near $r_{12}=0$ comes from the fact that,
as it is made of gaussian functions, $u^{\text{TN}}(r_{12})$ is cusp-less \textit{i.e.} 
\begin{equation}
 \lim_{r_{12}\rightarrow 0} \deriv{}{r_{12}}{}u^{\text{TN}}(r_{12}) = 0, 
\end{equation}
and as a necessary condition to obtain a non divergent scalar potential is 
\begin{equation}
 \label{eq:cusp_phi_0}
 \lim_{r_{12}\rightarrow 0} \deriv{}{r_{12}}{}u(r_{12}) = \frac{1}{2}, 
\end{equation}
(see Eqs. \eqref{eq:cusp_phi_0}  and \eqref{eq:cusp_phi_1} in Appendix \ref{sec:cusp}), $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ is necessary not bounded at $r_{12}=0$.  
%Because the condition of Eq. \eqref{eq:cusp_phi_0} is fulfilled by $u(r_{12},\mu)$ for all $\mu < \infty$, 
%the effective potential obtained by the similarity transformation of $H$ by $u(r_{12},\mu)$ is necessary non divergent.

@@

\begin{table*}
\label{table_conv_e_mu}
\caption{Ground state eigenvalue (in Hartree) of $\tilde{H}[\mu]$ for the He atom with the AVXZ (X=D,T,Q,5) basis sets for different values of $\mu$, and error (in mH) with respect to the exact non relativistic energy. 
We also compare with the results of the TC obtained with the $u(r_{12}) = u^{\text{TN}}(r_{12})$ (see Eq. \eqref{eq_frogg} and Ref.\onlinecite{TenNo-CPL-00-a}), referred here as FROGG, and the value of $\mfrogg=0.86975$ is defined in Eq. \eqref{mu_ten_no_1}. 
 }
\begin{ruledtabular}
\begin{tabular}{llllllllllll}
 Basis/$\mu$ & 0.2                   & 0.3                   & 0.35                  & 0.5                  & 0.7                 & $\mfrogg=0.86975$    \\
\hline                                                                                                                                                  
 AVDZ        &    -2.906309 (-2.58)  &    -2.904172 (-0.45)  &    -2.903317 (0.41)   &    -2.901420 (2.3)   &    -2.899516 (4.21) &  -2.897927 ( 5.80)    \\
 AVTZ        &    -2.905278 (-1.55)  &    -2.904691 (-0.97)  &    -2.904468 (-0.74)  &    -2.903969 (-0.24) &    -2.903488 (0.24) &  -2.903214 ( 0.51)    \\
 AVQZ        &    -2.904325 (-0.6)   &    -2.903986 (-0.26)  &    -2.903879 (-0.15)  &    -2.903702 (0.02)  &    -2.903620 (0.1)  &  -2.903589 ( 0.13)     \\
 AV5Z        &    -2.904229 (-0.51)  &    -2.903928 (-0.2)   &    -2.903834 (-0.11)  &    -2.903702 (0.02)  &    -2.903676 (0.05) &  -2.903678 (-0.1)     \\
\hline
 Basis/$\mu$ & 1.0                   & 1.6                   & 2.0                   & 3.0                  & $\infty$ (FCI)       &     $\frogg$        \\
\hline                                                                                                                                                   
 AVDZ        &    -2.896734 (6.99)   &    -2.892773 (10.95)  &    -2.891477 (12.25)  &    -2.890212 (13.51) &    -2.889548 (14.18) &    -2.897972 (5.75 )\\
 AVTZ        &    -2.903069 (0.66)   &    -2.902421 (1.3)    &    -2.901932 (1.79)   &    -2.901159 (2.56)  &    -2.900598 (3.13)  &    -2.903919 (-0.20)\\
 AVQZ        &    -2.903558 (0.17)   &    -2.903359 (0.36)   &    -2.903244 (0.48)   &    -2.902951 (0.77)  &    -2.902534 (1.19)  &    -2.903833 (-0.11)\\
 AV5Z        &    -2.903675 (0.05)   &    -2.903634 (0.09)   &    -2.903592 (0.13)   &    -2.903479 (0.24)  &    -2.903201 (0.52)  &    -2.903825 (-0.10)\\
\hline                                                                                                                                                   
\multicolumn{7}{c}{Exact non relativistic: -2.903724}   \\
\end{tabular}
\end{ruledtabular}
\end{table*}

>>>>

\begin{abstract}
The present work introduces a new form of explicitly correlated factor in the context of the transcorrelated methods. 
The new correlation factor is obtained from the $r_{12} \approx 0$ mathematical analysis of the transcorrelated Hamiltonian, and its analytical form is obtained such that the scalar part of the effective two-electron potential reproduces the long-range interaction of the range-separated density functional theory at leading order in $1/r_{12}$. 
The resulting correlation factor is then tuned by a unique parameter $\mu$ which controls both the depth of the coulomb hole and its typical range in $r_{12}$. 
The transcorrelated Hamiltonian obtained with such a new correlation factor as a straightforward analytical expression  depending on the same parameter $\mu$, and its physical contents continuously change by varying $\mu$ : one can change from a non divergent repulsive Hamiltonian at large $\mu$ to a purely attractive one at small $\mu$. We investigate the convergence of the eigenvalues and right-eigenvectors of such new transcorrelated Hamiltonian as a function of the basis set and as a function of $\mu$ on a series of two-electron systems. 
We found that the convergence towards the complete basis set is much faster for a quite wide range values of $\mu$. We also propose a computationally cheap way to find a reasonable value of $\mu$ that automatically adapts to the system through its density.  
It should be pointed out that all two-electron integrals can be carried analytically within such approach and the three-electrons terms can be performed using a mixed analytical-numerical integration approach.

@@

\subsection{A new form of Jastrow factor $u(\mu,r_{12})$ mimicking a long-range interaction}
\label{sec:new_j}
\subsubsection{A simple physical picture: the transcorrelated Hamiltonian for the helium atom}
\label{sec:he_htilde}
Let us write the Hamiltonian of the helium atom using the $r_i = \big|{\bf r}_i\big|$ and $ r_{12} = \big|{\bf r}_1 - {\bf r}_2 \big|$ coordinates\cite{Hylleraas-AdvQChem-64}  
\begin{equation}
 H  = h_c + \frac{1}{r_{12}},
\end{equation}
where 
\begin{equation}
 \begin{aligned}
 \label{def:h_c}
 h_c = &-\frac{1}{2} \sum_{i=1}^2 \bigg(\deriv{}{r_i}{2} + \frac{2}{r_i} \deriv{}{r_i}{} + \frac{2 Z}{r_i}\bigg) \\
     &-\bigg( \deriv{}{r_{12}}{2} + \frac{2}{r_{12}} \deriv{}{r_{12}}{} \bigg) \\
     &-\bigg( \frac{\bd{r_1}}{r_1} \cdot \frac{\bd{r_{12}} }{r_{12}}  \deriv{}{r_1}{} + 
                \frac{\bd{r_2}}{r_2} \cdot \frac{\bd{r_{21}} }{r_{21}}  \deriv{}{r_2}{} \bigg).
 \end{aligned}
\end{equation}
\label{sec:he_j}
Now let us consider the transcorrelated Hamiltonian $\tilde{H}[u]$ obtained by a similarity transformation of the usual Hamiltonian by a Jastrow factor $u(r_{12})$ depending only on $r_{12}$: 
\begin{equation}
 \label{eq:ht_0}
 \begin{aligned}
 \tilde{H}[u]&= e^{-u(r_{12})} H e^{u(r_{12})}.
 \end{aligned}
\end{equation}
The only additional terms arising in $\tilde{H}[u]$ with respect to $H$ are those coming from the action of the differential operator in $r_{12}$,
\begin{equation}
 \mathcal{T}[u] =  -e^{-u(r_{12})}\bigg( \deriv{}{r_{12}}{2} + \frac{2}{r_{12}} \deriv{}{r_{12}}{} \bigg)e^{u(r_{12})}.  
\end{equation}
By defining the following operators 
\begin{equation}
 \label{eq:def_tt}
 \tilde{t}[u] = -2 \deriv{u(r_{12})}{r_{12}}{} \deriv{}{r_{12}}{},
\end{equation}
\begin{equation}
 \label{eq:def_wt}
 \tilde{W}[u] = -\frac{2}{r_{12}} \deriv{u(r_{12})}{r_{12}}{}  , 
\end{equation}
\begin{equation}
 \label{eq:def_wt}
 \tilde{w}[u] = -\deriv{u(r_{12})}{r_{12}}{2} - \bigg( \deriv{u(r_{12})}{r_{12}}{} \bigg)^2, 
\end{equation}
one can write the Similarity transformed Hamiltonian  as
\begin{equation}
 \label{eq:ht_general}
 \tilde{H}[u] = h_c + \frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u] + \tilde{t}[u].
\end{equation}
Therefore, one can see from Eq. \eqref{eq:ht_general} that the two electrons experience a modified scalar potential given by $\frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u]$, and an additional differential operator $\tilde{t}[u]$, 
the latter making $\tilde{H}[u]$ non-hermitian.

\subsubsection{The working equation for $u(\mu,r_{12})$ inspired by RSDFT}
Having established the form of $\tilde{H}[u] $ in Eq. \eqref{eq:ht_general}, one can notice that the leading order terms in $1/r_{12}$ are $\frac{1}{r_{12}}  + \tilde{W}[u]$. We want now to impose the form of $u(r_{12})$ such that it mimics, at leading order in $1/r_{12}$, the long-range effective interaction entering in the effective Hamiltonian of the RS-DFT (see Eq. \eqref{eq:cusp_psi_mu_0} in Appendix \ref{sec:cusp}). 
Mathematically, this condition implies that 
\begin{equation}
 \begin{aligned}
 \label{def_j_00}
 \tilde{W}[u] + \frac{1}{r_{12}}&= \frac{\text{erf}(\mu r_{12})}{r_{12}} \\ 
\Leftrightarrow -\frac{2}{r_{12}} \deriv{u(r_{12},\mu)}{r_{12}}{} + \frac{1}{r_{12}} & = \frac{\text{erf}(\mu r_{12})}{r_{12}}, 
 \end{aligned}
\end{equation}
which is equivalent to 
\begin{equation}
 \label{def_j_0}
 \deriv{u(r_{12},\mu)}{r_{12}}{} = \frac{1 - \text{erf}(\mu r_{12})}{2}.
\end{equation}
The solution to Eq. \eqref{def_j_0} is 
\begin{equation}
 \label{eq:def_j}
 u(r_{12};\mu) = \frac{1}{2}r_{12}\bigg( 1 - \text{erf}(\mu r_{12})  \bigg) - \frac{1}{2\sqrt{\pi}\mu}e^{-(r_{12}\mu)^2},
\end{equation}
which defines the new Jastrow factor $u(r_{12};\mu)$ which depends on a unique parameter $\mu$.

@@

\subsection{The general analytical form of  $\tilde{H}[\mu]$ and some of its properties}
\label{sec:ht_general}
\subsubsection{General analytical form of $\tilde{H}[\mu]$ for a $N$-electron system}

Having established the analytical expression of $u(r_{12};\mu)$, one can derive the expression of the associated transcorrelated Hamiltonian for a general $N$-electron system.  
Using the general form of the transcorrelated Hamiltonian of Eq. (2) in Ref. \onlinecite{CohLuoGutDobTewAla-JCP-19} and using $u(r_{12},\mu)$ as Jastrow factor gives 
\begin{equation}
 \begin{aligned}
 \label{ht_def_g}
 \tilde{H}[\mu] &\equiv e^{-\hat{\tau}_\mu} \hat{H} e^{\hat{\tau}_\mu} \\ 
                &= H + \big[ H,\hat{\tau}_\mu \big] + \frac{1}{2}\bigg[ \big[H,\hat{\tau}_\mu\big],\hat{\tau}_\mu\bigg],
 \end{aligned}
\end{equation}
with $\hat{\tau}_\mu = \sum_{i<j}u(r_{ij},\mu)$ and $\hat{H} = \sum_i -\frac{1}{2} \nabla^2_i + v(\br{}_i) + \sum_{i<j} \frac{1}{r_{ij}}$. 
Therefore, the right- and left-eigenvectors of $\tilde{H}[\mu]$ depends only on $\mu$, and the right-eigenvectors satisfy 
\begin{equation}
 \tilde{H}[\mu] \phimui(\br{}_{1},\br{}_{2}) = E_i \phimui(\br{}_{1},\br{}_{2}), 
\end{equation}
where $E_i$ is the exact $i$-th eigenvalue of the physical Hamiltonian. The fact that $\tilde{H}[\mu]$ and $H$ have the same spectrum originates from the properties of the similarity transformation. Nevertheless, once projected in an incomplete basis set, $\tilde{H}[\mu]$ and $H$ might not have the same eigenvalues.

Eq. \eqref{ht_def_g} leads to the following transcorrelated Hamiltonian 
\begin{equation}
 \begin{aligned}
 \label{ht_def_gu}
 \tilde{H}[\mu] & = H - \sum_{i<j} \hat{K}_\mu(\bri{i},\bri{j}) - \sum_{i<j<k} \hat{L}_\mu(\bri{i},\bri{j},\bri{k}),
 \end{aligned}
\end{equation}
where the effective two- and three-body operators $\hat{K}_\mu(\bri{1},\bri{2})$ and $\hat{L}_\mu(\bri{1},\bri{2},\bri{3})$ are defined as
\begin{equation}
 \begin{aligned}
 \label{def_k}
  \hat{K}_\mu(\bri{1},\bri{2})  = \frac{1}{2} \bigg( &\Delta_1 u(r_{12},\mu) + \Delta_2 u(r_{12},\mu) \\
                                               + &\big(\nabla_1 u(r_{12},\mu) \big) ^2 + \big(\nabla_1 u(r_{12},\mu) \big) ^2 \bigg) \\
                                               + &\nabla_1 u(r_{12},\mu) \cdot \nabla_2 + \nabla_2 u(r_{12},\mu)\cdot \nabla_1,
 \end{aligned}
\end{equation}
\begin{equation}
 \begin{aligned}
 \label{def_k}
  \hat{L}_\mu(\bri{1},\bri{2},\bri{3})  = & \nabla_1 u(r_{12},\mu) \cdot \nabla_1 u(r_{13},\mu) + \nabla_2 u(r_{21},\mu) \cdot \nabla_2 u(r_{23},\mu)  \\
                                     + & \nabla_3 u(r_{13},\mu) \cdot \nabla_3 u(r_{32},\mu).
 \end{aligned}
\end{equation}

@@

\subsubsection{A special case of $\tilde{H}[\mu]$ which mimics the FROGG}
As the Jastrow factor $u(r_{12},\mu)$ for $\mu=\mfrogg$ is very close to the FROGG, we can also compare the scalar effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ with that obtained with the transcorrelated Hamiltonian obtained with the FROGG. 
The latter is simply defined as 
\begin{equation}
 \label{eq:tn_htilde}
 \tilde{H}_{\text{TN}} = e^{-\hat{\tau}_{\text{TN}}}H e^{\hat{\tau}_{\text{TN}}},
\end{equation}
with $\hat{\tau}_{\text{TN}} = \sum_{i<j} u^\text{TN}(r_{ij})$. 
This leads to the following transcorrelated Hamiltonian 
\begin{equation}
 \label{eq:tn_htilde_2}
  \tilde{H}_{\text{TN}} = H + \sum_{i<j} \bigg( \tilde{\mathcal{W}}^\text{TN}_{ee}(r_{ij}) + \tilde{t}^\text{TN} \bigg) - \sum_{i<j<k} \hat{L}^\text{TN}(\bri{1},\bri{2},\bri{3})
\end{equation}
where 
\begin{equation}
 \label{eq:_wee_frogg}
 \tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})= \frac{1}{r_{12}}-\Delta_1 u^{\text{TN}}(r_{12}) - \big(\nabla_1 u^{\text{TN}}(r_{12}) \big) ^2, 
\end{equation}
\begin{equation}
 \begin{aligned}
 \tilde{t}^\text{TN} = &\nabla_1 u^\text{TN}(r_{12}) \cdot \nabla_2 + \nabla_2 u^\text{TN}(r_{12})\cdot \nabla_1,
 \end{aligned}
\end{equation}
\begin{equation}
 \begin{aligned}
 \label{def_k}
  \hat{L}^{\text{TN}}(\bri{1},\bri{2},\bri{3})  = & \nabla_1 u^\text{TN}(r_{12}) \cdot \nabla_1 u^\text{TN}(r_{12}) \\ 
                                     + & \nabla_2 u^\text{TN}(r_{21}) \cdot \nabla_2 u^\text{TN}(r_{23})  \\
                                     + & \nabla_3 u^\text{TN}(r_{31}) \cdot \nabla_3 u^\text{TN}(r_{32}).
 \end{aligned}
\end{equation}
As apparent from Fig. \ref{fig_wee_frogg} where $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ and $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ are represented, while the latter is perfectly smooth for all $r_{12}$, the former strongly oscillates near $r_{12}=0$ between positive and negative values and is not bounded for $r_{12}=0$. 
Such behaviour of $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ near $r_{12}=0$ comes from the fact that,
as it is made of gaussian functions, $u^{\text{TN}}(r_{12})$ is cusp-less \textit{i.e.} 
\begin{equation}
 \lim_{r_{12}\rightarrow 0} \deriv{}{r_{12}}{}u^{\text{TN}}(r_{12}) = 0, 
\end{equation}
and as a necessary condition to obtain a non divergent scalar potential is 
\begin{equation}
 \label{eq:cusp_phi_0}
 \lim_{r_{12}\rightarrow 0} \deriv{}{r_{12}}{}u(r_{12}) = \frac{1}{2}, 
\end{equation}
(see Eqs. \eqref{eq:cusp_phi_0}  and \eqref{eq:cusp_phi_1} in Appendix \ref{sec:cusp}), $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ is necessary not bounded at $r_{12}=0$.

@@

\begin{table*}
\label{table_conv_e_mu}
\caption{Ground state eigenvalue (in Hartree) of $\tilde{H}[\mu]$ for the He atom with the AVXZ (X=D,T,Q,5) basis sets for different values of $\mu$, and error (in mH) with respect to the exact non relativistic energy. 
We also compare with the results of the TC obtained with the $u(r_{12}) = u^{\text{TN}}(r_{12})$ (see Eq. \eqref{eq_frogg} and Ref.\onlinecite{TenNo-CPL-00-a}), referred here as FROGG, and the value of $\mfrogg=0.86975$ is defined in Eq. \eqref{mu_ten_no_1}. The exact non relativistic energy was obtained from Ref. \cite{Dav-ions-PRA-91}. 
 }
\begin{ruledtabular}
\begin{tabular}{llllllllllll}
 Basis/$\mu$ & 0.2                   & 0.3                   & 0.35                  & 0.5                  & 0.7                 & $\mfrogg=0.86975$    \\
\hline                                                                                                                                                  
 AVDZ        &    -2.906309 (-2.58)  &    -2.904172 (-0.45)  &    -2.903317 (0.41)   &    -2.901420 (2.3)   &    -2.899516 (4.21) &  -2.897927 ( 5.80)    \\
 AVTZ        &    -2.905278 (-1.55)  &    -2.904691 (-0.97)  &    -2.904468 (-0.74)  &    -2.903969 (-0.24) &    -2.903488 (0.24) &  -2.903214 ( 0.51)    \\
 AVQZ        &    -2.904325 (-0.6)   &    -2.903986 (-0.26)  &    -2.903879 (-0.15)  &    -2.903702 (0.02)  &    -2.903620 (0.1)  &  -2.903589 ( 0.13)     \\
 AV5Z        &    -2.904229 (-0.51)  &    -2.903928 (-0.2)   &    -2.903834 (-0.11)  &    -2.903702 (0.02)  &    -2.903676 (0.05) &  -2.903678 (-0.1)     \\
\hline
 Basis/$\mu$ & 1.0                   & 1.6                   & 2.0                   & 3.0                  & $\infty$ (FCI)       &     $\frogg$        \\
\hline                                                                                                                                                   
 AVDZ        &    -2.896734 (6.99)   &    -2.892773 (10.95)  &    -2.891477 (12.25)  &    -2.890212 (13.51) &    -2.889548 (14.18) &    -2.897972 (5.75 )\\
 AVTZ        &    -2.903069 (0.66)   &    -2.902421 (1.3)    &    -2.901932 (1.79)   &    -2.901159 (2.56)  &    -2.900598 (3.13)  &    -2.903919 (-0.20)\\
 AVQZ        &    -2.903558 (0.17)   &    -2.903359 (0.36)   &    -2.903244 (0.48)   &    -2.902951 (0.77)  &    -2.902534 (1.19)  &    -2.903833 (-0.11)\\
 AV5Z        &    -2.903675 (0.05)   &    -2.903634 (0.09)   &    -2.903592 (0.13)   &    -2.903479 (0.24)  &    -2.903201 (0.52)  &    -2.903825 (-0.10)\\
\hline                                                                                                                                                   
\multicolumn{7}{c}{Exact non relativistic: -2.903724}   \\
\end{tabular}
\end{ruledtabular}
\end{table*}
